The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-06 registry.tex
Add poliastro citation

\href{https://github.com/poliastro/poliastro}{poliastro} & No & \href{https://pypi.python.org/pypi/poliastro}{poliastro} & Juan Luis Cano Rodríguez &  \\

>>>>

\href{https://github.com/poliastro/poliastro}{poliastro} & No & \href{https://pypi.python.org/pypi/poliastro}{poliastro} & Juan Luis Cano Rodríguez & \citealt{poliastro} \\
